Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-03-17 manuscript.tex
modifying
to stability analysis
now, numerical and real-system implementation validations are desired.

\newcommand*{\fe}{\mv r}

\newcommand*{\q}{\mv q}
\newcommand*{\dq}{\dot{\mv q}}
\newcommand*{\ddq}{\ddot{\mv q}}
\newcommand*{\qd}{\mv q_d}
\newcommand*{\dqd}{\dot{\mv q_d}}
\newcommand*{\ddqd}{\ddot{\mv q_d}}

\newcommand*{\NN}{\mv\Phi}
\newcommand*{\act}{\mv\phi}
\newcommand*{\wth}{\mv\theta}
\newcommand*{\wV}{\mm W}

\newcommand*{\estwth}{\widehat\wth}
\newcommand*{\estNN}{\widehat\NN}
\newcommand*{\estact}{\widehat\act}
\newcommand*{\estwV}{\widehat\wV}

\newcommand*{\idealwth}{\wth^*}
\newcommand*{\idealNN}{\NN^*}
\newcommand*{\idealact}{\act^*}
\newcommand*{\idealwV}{\wV^*}

@@

In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
Considering the control input saturation function, $\qd(t)$ is supposed to be available to design a feasible control input in the presence of the control input saturation.

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \dot{V}_1
        =&
        \fe^\top \mm M (
            -\mm V_m \fe -\mm K \fe + \mv f
            -\mv \tau_d + \sat(\mv\tau)
        )
        +
        \tfrac{1}{2}
        \fe^\top \dot{\mm M}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\sat(\mv\tau)
            -\mv \tau_d
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
        \\
        \le&
        -\lambda_\text{min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\sat(\mv \tau))
        \\
        \le&
        -\lambda_\text{min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\sat(\mv\tau)-\mv\tau^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\mv\tau^*:= -\mv f$ is the ideal control input. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_\text{min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
\begin{equation}
    \wth := 
    \begin{bmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{bmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
        &
        i=k 
        \\
        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
        & 
        i=k-1
        \\
        &
        \vdots 
        \\
        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
        &
        i = 0
    \end{cases},
\end{equation}
where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

\begin{remark}
    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in pracice including the origin.
    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
\end{remark}

The following Lemma is introduced for the stability analysis. % of the last layer of the DNN.
\begin{lem}
    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
    \label{lem:convex:angle}
\end{lem}

@@

Since $\mv\tau = -\estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
\begin{equation}\label{eq:linear:map}
    \begin{aligned}
    \mv\tau 
    = 
    &
    -\estNN 
    % = 
    % -\myvec(\estNN)
    =
    -\myvec(
        \estwV_k^\top \estact_k
    ) 
    = 
    -(
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top
    \myvec(\estwV_k)
    \\
    = &
    -\underbrace{
        (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top}_{:=\mm T(\estact_k)}
    \estwth_k 
    =
    \mm T(\estact_k) \estwth_k.
    \end{aligned}
\end{equation}
Therefore, the convexity of the input constraints in $\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \Vert \estwth_i\Vert^2 
    -
    \bar\theta_i^2 \le 0
    \label{eq:cstr:weight_ball}
\end{equation}
with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        2\estwth_i,
        &
        \text{if } i=j
        \\
        0,
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight_ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.

@@

% \begin{lem} 
%     If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum1}, then $\Vert\partial c_j/\partial\estwth_i\Vert$, for all $i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i$, for all $i\in[k,\cdots, i+1]$, remain bounded.
%     % which can be verified using the boundedness of $\estwth_i,\ \forall i [k,\cdots,i+1]$ (as demonstrated in Section \ref{sec:stability}), and the boundedness of $\Vert\phi_i(\cdot)\Vert$ and $\Vert\nabla\phi_i(\cdot)\Vert$.
%     \label{lem2}
% \end{lem}

% \begin{proof}

% The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
% \begin{equation}
%     {\partial c_j\over\partial \estwth_i} = {\partial c_j\over\partial \tau} {\partial \tau\over\partial \hat\Phi} {\partial \hat\Phi\over\partial \estwth_i}
% \end{equation}
% where $\partial \tau/\partial \hat\Phi=-I_n$, which is bounded. From the linear mapping in \eqref{eq linear map}, $\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\Vert\phi_k(\cdot)\Vert$ is bounded due to the properties of the activation functions. By Assumption \ref{assum1}, the function $c_j$ is convex. The convex function has a bounded derivative with respect to $\tau$, since $\tau$ is a bounded variable (\ie $\partial c_j/\partial\tau$ is bounded). Furthermore, $\partial \hat\Phi/\partial \estwth_i$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. This can be verfied by using the definition of $\partial \hat\Phi/\partial\estwth_i$ given in \eqref{eq. nabla phi}.
% Consequently, $\Vert\partial c_j/\partial \estwth_i\Vert,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.

% \end{proof}

Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
The following theorem shows that $\estwth$ and $\fe$ are bounded.

@@

The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ is supposed to be active.
This assumption is reasonable, since even if the constraint is inactive \MSRY{Add the reason why it is reasonable.}
The step-by-step analysis is described as follows.
\MSRY{start from here plz}
\subsection*{Step 1: Boundedness of $\estwth_k$, and $\fe$}

% As the result of the time derivative of $V_1$, the radius of invariant set $\Theta_\fe^{c_1}$ of $\fe$ can be obtained as

Assume that all constraints are actve in $\mathcal A$ without loss of generality. The dynamics of $\eta_k$ and $\estwth_k$ can be decomposed from \eqref{eq. adaptation law th} and \eqref{eq. eta dynamics} as 
\begin{equation}
    \begin{aligned}
        \dot\eta_k =
        & 
        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}{\partial \hat\Phi\over \partial \estwth_k}
        =
        A_\xi \eta_k -B_\xi {\partial h\over\partial\tau}(I_{l_{k+1}}\otimes \hat\phi_k^\top)\\
        \dot{\estwth}_k =
        & -\alpha 
        \bigg[
            \eta_k^\top W\xi+
            \sum_{j\in\mathcal{A}}
            \lambda_j{\partial c_j\over\partial \estwth_k}
        \bigg]
    \end{aligned} 
\end{equation}
According to \cite[Chap.~4 T.~1.9]{Desoer:2009aa}, $\Vert \eta_k\Vert_F$ is bounded, since $A_\xi$ is a stable matrix and the term $-B_\xi(\partial h/\partial \tau)(I_{l_{k+1}}\otimes\hat\phi_k^\top)$ is also bounded.

Let $\mathcal{V}: \R^{2n} \times \R^{\Xi} \to \R_{>0}$ denote the Lyapunov function:
\begin{equation}
    \mathcal{V} = \frac{1}{2} \xi^\top P \xi + \frac{1}{2 \alpha} \hat{\wth}_k^\top \hat{\wth}_k,
    \label{eq. Lyapunov func}
\end{equation}
with the Lyapunov equation $A_\xi^\top P + P A_\xi = -Q$, where $A_\xi < 0$, $P = P^\top > 0$, and $Q > 0$.
Taking the time derivative of $\mathcal{V}$ yields:
\begin{equation}
    \begin{aligned}
        \dot{\mathcal{V}} 
        &= -\frac{1}{2} \xi^\top Q \xi + \xi^\top P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon) \\
        &\quad - \hat{\wth}_k^\top \left( \eta_k W \xi + \sum_{j \in \mathcal{A}} \lambda_j \frac{\partial c_j}{\partial \hat{\wth}_k} \right)
    \end{aligned}
    \label{eq. Lyapunov dot}
\end{equation}
By applying the boundedness of $\Delta := P B (V_k^{*T} \phi_k^* - h(\tau) + \epsilon)$ and $M := \eta_k W$, where $\Vert \Delta \Vert \leq \bar{\Delta} < \infty$ and $\Vert M \Vert_F \leq \bar{M} < \infty$, this simplifies to:
\begin{equation}
    \begin{aligned}
        \dot{\mathcal{V}} 
        &\leq \left( -\frac{\lambda_{\text{min}}(Q)}{2} + \frac{\bar{M}}{2} \right) \Vert \xi \Vert^2 + \bar{\Delta} \Vert \xi \Vert \\
        &\quad + \frac{\bar{M}}{2} \Vert \hat{\wth}_k \Vert^2 - \sum_{j \in \mathcal{A}} \lambda_j \hat{\wth}_k^\top \frac{\partial c_j}{\partial \hat{\wth}_k}.
    \end{aligned}
    \label{eq. dot Vk 1}
\end{equation}

>>>>

\newcommand*{\fe}{\mv{r}}

\newcommand*{\q}{\mv{q}}
\newcommand*{\dq}{\dot{\mv q}}
\newcommand*{\ddq}{\ddot{\mv q}}
\newcommand*{\qd}{\mv{q_d}}
\newcommand*{\dqd}{\dot{\mv q_d}}
\newcommand*{\ddqd}{\ddot{\mv q_d}}

\newcommand*{\NN}{\mv{\Phi}}
\newcommand*{\act}{\mv{\phi}}
\newcommand*{\wth}{\mv{\theta}}
\newcommand*{\wV}{\mm{W}}

\newcommand*{\estwth}{\widehat{\wth}}
\newcommand*{\estNN}{\widehat{\NN}}
\newcommand*{\estact}{\widehat{\act}}
\newcommand*{\estwV}{\widehat{\wV}}

\newcommand*{\idealwth}{{\wth}^*}
\newcommand*{\idealNN}{{\NN}^*}
\newcommand*{\idealact}{{\act}^*}
\newcommand*{\idealwV}{{\wV}^*}

@@

In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
\begin{assum}
    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \bar{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
    \label{assum:feasible}
\end{assum}

@@

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \mm M (
            -\mm V_m \fe -\mm K \fe + \mv f
            -\mv \tau_d + \sat(\mv\tau)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\mm M}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\sat(\mv\tau)
            -\mv \tau_d
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
        \\
        \le&
        -\lambda_\text{min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\sat(\mv \tau))
        \\
        \le&
        -\lambda_\text{min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\sat(\mv\tau)-\mv\tau^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and \eqref{eq:sat}. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_\text{min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.

@@

For simplicity, each layer's weights are vectorized as $\wth_i:=\myvec(\wV_i)\in\R^{\Xi_i}$, where $\Xi_i:= (l_i+1)l_{i+1}$ is the number of weights in the $i\textsuperscript{th}$ layer. 
The total weight vector $\wth\in\R^{\Xi}$ is defined by augmenting $\wth_i$ for all $i\in [0,\cdots,k]$ as 
\begin{equation}
    \wth := 
    \begin{bmatrix}
        \wth_k\\
        \wth_{k-1}\\
        \vdots\\
        \wth_0
    \end{bmatrix}
    =
    \begin{bmatrix}
        \myvec(\wV_k)\\
        \myvec(\wV_{k-1})\\
        \vdots\\
        \myvec(\wV_0)
    \end{bmatrix},
\end{equation}
where $\Xi={\sum_{i=0}^{k} \Xi_i}$ represents the total number of weights. The gradient of $ \NN(\q_{NN};\wth)$ with respect to $\wth$ is defined as
\begin{equation}
    \pptfrac{\NN}{\wth}=
    \begin{bmatrix}
        \pptfrac{\NN}{\wth_k}&
        \pptfrac{\NN}{\wth_{k-1}}&
    \cdots &
        \pptfrac{\NN}{\wth_0}
    \end{bmatrix}
    \in\R^{n \times \Xi}
    \label{eq. nabla phi}
\end{equation}
where
\begin{equation}
    \pptfrac{\NN}{\wth_i} = 
    \begin{cases}
        (\mm I_{l_{k+1}}\otimes \act_{k}^\top  ), 
        &
        i=k 
        \\
        \wV_k^\top   \act_{k}' (\mm I_{l_{k}}\otimes  \act_{k-1}^\top  ), 
        & 
        i=k-1
        \\
        &
        \vdots 
        \\
        \wV_k^\top   \act'_{k} \cdots \wV_1^\top  \act_1' (\mm I_{l_1}\otimes \q_{NN}^\top  ), 
        &
        i = 0
    \end{cases},
    \label{eq:NN:grad}
\end{equation}
where $\act_i:= \act_i(\NN_{i-1})$ and $\act_i':= \pptfrac{\act_i}{\NN_{i-1}}$.

@@

\begin{remark}
    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in practice including the origin.
    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
\end{remark}

The following Lemma is introduced for the stability analysis.
\begin{lem}
    If Assumptions \ref{assum:convex} and \ref{assum:LICQ} are satisfied, the angle between $\pptfrac{c_j}{\estwth_k}$ and $\estwth_k$ is positive when $c_j$ is active, \ie $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.
    \label{lem:convex:angle}
\end{lem}

@@

Since $\mv\tau = \estNN$, using \cite[Proposition 7.1.9]{Bernstein:2009aa}, a linear map $\mm T(\cdot):\estwth_k\to\mv\tau$ can be derived: 
\begin{equation}\label{eq:linear:map}
    \begin{aligned}
    \mv\tau 
    = 
    &
    \estNN 
    % = 
    % \myvec(\estNN)
    =
    \myvec(
        \estwV_k^\top \estact_k
    ) 
    = 
    (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top
    \myvec(\estwV_k)
    \\
    = &
    \underbrace{
        (
        \mm I_{l_{k+1}}
        \otimes 
        \estact_k^\top
    )^\top}_{:=\mm T(\estact_k)}
    \estwth_k 
    =
    \mm T(\estact_k) \estwth_k.
    \end{aligned}
\end{equation}
Therefore, the convexity of the input constraints in $\mv\tau$-space (assumed in Assumption \ref{assum:convex}) holds in $\estwth_k$-space, implying
that $\pptfrac{c_j}{\estwth_k}^\top\estwth_k>0$.

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    (
        \Vert \estwth_i\Vert^2 
        -
        \bar\theta_i^2 
    )    
    \le 0
    \label{eq:cstr:weight_ball}
\end{equation}
with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j
        \\
        0,
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight_ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.

@@

Before conducting the stability analysis, let us define the weight estimation error as $\tilde\wth:= [\tilde\wth_i]_{i\in[0,\cdots,k]}$, where $\tilde\wth_i:=\estwth_i-\idealwth_i$.
The following lemma is introduced for the stability analysis.

\begin{lem} 
    If $c_j(\estwth),\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ satisfies Assumption \ref{assum:convex}, then $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall i\in[k-1,\cdots, 0]$, is bounded, provided the norms of $\estwth_i,\ \forall i\in[k,\cdots, i+1]$, remain bounded.
    \label{lem:cstr:grad:bound}
\end{lem}

The derivative of $c_j,\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, with respect to $\estwth_i$ is represented as
\begin{equation}
    \pptfrac{c_j}{\estwth_i} 
    = 
    \pptfrac{c_j}{\mv\tau} 
    \pptfrac{\mv\tau}{\estNN} 
    \pptfrac{\estNN}{\estwth_i}
\end{equation}
where $\pptfrac{\tau}{\estNN}=\mm I_n$, which is bounded. 
From the linear mapping in \eqref{eq:linear:map}, $\mv\tau$ is bounded as long as $\estwth_k$ is bounded (by the condition of the lemma), and $\norm{\act_k(\cdot)}$ is bounded due to the properties of the activation functions. 
By Assumption \ref{assum:convex}, the function $c_j$ is convex. 
The convex function has a bounded derivative with respect to $\mv\tau$, since $\mv\tau$ is a bounded variable (\ie $\pptfrac{c_j}{\mv\tau}$ is bounded). 
Furthermore, $\pptfrac{\estNN}{\estwth_i}$ is bounded, provided that the norms of $\estwth_i,\ \forall i \in[k,\cdots,i+1]$, are bounded. 
This can be verified by using the definition of $\pptfrac{\estNN}{\estwth_i}$ given in \eqref{eq:NN:grad}.
Consequently, $\norm{\pptfrac{c_j}{\estwth_i}},\ \forall j\in\mathcal I \setminus \{\wth_i\}_{i\in[0,\cdots,k]}$, is bounded, when $\estwth_i,\ \forall i\in [k,\cdots,i+1]$ are bounded.

The following theorem shows that $\estwth$ and $\fe$ are bounded.

@@

The boundednesses of $\estwth$ and $\fe$ are analyzed recursively from the last $k\textsuperscript{th}$ layer to the first layer of $\estNN$. 
Without loss of generality, weight constraint $c_{\theta_i},\ \forall i\in[0,\cdots,k]$ is supposed to be active.
This assumption is reasonable, since even if the constraint is inactive 
\MSRY{Add the reason why it is reasonable.}
We consider two cases: (C$_1$) control input constraints are active, and (C$_2$) control input constraints are inactive.
Using the fact that amplitude of the control input is only depends on $\estwth_k$ (\ie see \eqref{eq:control:est}, \eqref{eq:DNN:architecture} and $\norm{\act_k}<\infty$), the boundedness of inner layers' weights will be verified after the boundedness of $\estwth_k$ and $\fe$ is confirmed.

\subsection*{Case (C$_1$): Control input constraints are active.}

As the result of the time derivative of $V_1$, the invariant set $\Theta_{\fe}^{c_1}$ of $\fe$ (\ie if $\fe$ leaves $\Theta_{\fe}^{c_1}$, $\ddtt V_1$ is negative) can be obtained as 
\begin{equation}
    \Theta_{\fe}^{c_1} 
    = 
    \left\{ 
        \fe \in \R^n 
        \mid 
        \norm{\fe} 
        \le 
        \tfrac{2\bar\tau+\bar\tau_d}{\lambda_{\text{min}}(\mm K)}
    \right\}
    .
    \label{eq:invariant:c1:fe}
\end{equation}

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
        }_{:=c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\bar\tau+\bar\tau_d)
        }{
            \lambda_{\theta_k}\lambda_\text{min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

The satisfaction of the constraints can be verified by the boundedness of $\estwth_k$.
For $c_{\theta_k}$, if the corresponding Lagrange multiplier $\lambda_{\theta_k}$ increases infinitely by the constraint violation, $\estwth_k$ approaches to the origin as $\Theta_{\estwth_k}^{c_1}$ is squeezed to a point.
The satisfactions of the remaining control input constraints can be verified implicitly using $c_2$ in \eqref{eq:lya2:dot}.
Similarly to $c_{\theta_k}$, as the control input constraint $c_j,\ \forall j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}$ is violated, the corresponding Lagrange multiplier $\lambda_j$ increases infinitely, so does $c_2$.
It makes $c_2$ dominates the right-hand side of \eqref{eq:lya2:dot}, which leads $\ddtt V_2$ negative definite.
This drives $\estwth_k$ to the origin until the constraint is satisfied (\ie by Assumption \ref{assum:convex} and Lemma \ref{lem:convex:angle}, the control input constraints can be considered as convex constraint in $\estwth_k$-space).

Therefore, the boundedness of $\estwth$ and $\fe$ are guaranteed by the invariant sets $\Theta_{\fe}^{c_1}$ and $\Theta_{\theta_k}^{c_1}$ and satisfactions of $c_j,\ \forall j\in\mathcal{I}$ are confirmed.

\subsection*{Case (C$_2$): Control input constraints are inactive.}

Since, here, the control input constraints are inactive, $\sat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
\begin{equation}
    \begin{aligned}
        \ddtt V_3
        =&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +\bar\tau_d\norm{\fe}
        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
        \\
        &
        -\estwth_k^\top (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        )
        \\
        \le&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +\fe^\top \estNN
        +(
            \bar\tau_d+\norm{
                \underbrace{
                    \idealNN+\mv\epsilon
                }_{=\mv\tau^*}
            }
        )
        \norm{\fe}
        \\
        &
        -\estNN^\top\fe 
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        \\
        \le&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +\fe^\top \estNN
        +(\bar\tau_d+\bar\tau)
        \norm{\fe}
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        .
    \end{aligned}
    \label{eq:lya3:dot}
\end{equation}
Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
\begin{equation}
    \Theta_{\fe}^{c_2}
    =
    \left\{ 
        \fe \in \R^n 
        \mid 
        \norm{\fe} 
        \le 
        \tfrac{
            \bar\tau_d+\bar\tau
        }{
            \lambda_{\text{min}}(\mm K)
        }
    \right\}
    .
\end{equation}
The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \bar\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.

\hfill

The boundedness of inner layers' weights and satisfactions of their constraints $c_j,\ \forall j\in\{\theta_i\}_{i\in[k-1,\cdots,0]}$ can be shown recursively, using \cite[Chap.~4 T.~1.9]{Desoer:2009aa}
The dynamics of $\estwth_i,\ \forall i\in[k-1,\cdots,0]$ are represented as
\begin{equation}
    \ddtt \estwth_i 
    =
    -\alpha
    (
        \pptfrac{\estNN}{\estwth_i}^\top
        \fe
        +
        \lambda_{\theta_i}\estwth_i
        +
        \textstyle\sum_{
            j\in\mathcal{A}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
        }
        \lambda_j
        \pptfrac{c_j}{\estwth_i}
    )
    .
\end{equation}
Invoking Lemma \ref{lem:cstr:grad:bound}, $\estwth_i$ is bounded, provided that $\estwth_i,\ \forall i\in[k,\cdots,i+1]$ are bounded, since the system matrix $-\lambda_{\theta_i} \mm I_{\Xi_i}$ is stable and the residual terms are bounded.
Therefore, starting from $(k-1)\textsuperscript{th}$ layer, the boundedness of $\estwth_i$ can be established recursively down to the input layer ($i=0$).

\hfill

Finally, the filtered error $\fe$ and the estimated weights $\estwth$ are bounded and the imposed constraints $c_j,\ \forall j\in\mathcal I$ are satisfied.
